Information Retrieval - Submission Report \\Project N.14: Art For Sale

### 2023-12-09 docs/report/submission.tex
feat: report added features description
Co-authored-by: Filippo Piloni <pilonf@usi.ch>

Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

    \subsection{Features}
    For this project, the following features have been implemented:
    \begin{itemize}
        \item Result presentation
        \item Filtering
        \item Automatic recommendation
    \end{itemize}

>>>>

    \subsection{Features}
    The course project requires 2 additional categorized features to be implemented besides the retrieval system:
    1 each from simple and complex group features.

    The following features have been implemented:
    \begin{itemize}
        \item Simple
              \begin{itemize}
                  \item \textbf{Result presentation}:
                        results should be presented in a tabular format so that many results could be seen at the same time.
                        Each table cell should contain appropriate information for your project.
                  \item \textbf{Filtering}:
                        in addition to being able to search by title, an user should be able to filter the
                        results based on at least 3 relevant attributes for your project.
              \end{itemize}

        \item Complex
              \begin{itemize}
                  \item \textbf{Automatic recommendation}:
                        In addition to the relevant search results pertaining to the user query,
                        the user should also be suggested "similar" products based on, say, category, description,
                        price etc. The ordering among the recommended items is not important.
                        However, you should mention how did you arrive at the recommendations.
                        For this purpose, you can use any open-source recommenders available.
              \end{itemize}
    \end{itemize}
